\textit{Supplemental Information:}\\ Design Principles from Glass Sponges \\for Structurally Robust Lattices

### 2018-12-05 Paper-FernandesWeaverBertoldi_AdvMaterials_2018.tex
changes

The macro-scale architecture of the \textit{Euplectella Asperguillum} provides a remarkable example of slender and regular lattice-like material constructed by nature. Such lattice materials have recently demonstrated to offer novel and unique properties, including being light weight, \cite{schaedler2011,ashby2006} having high energy absorption, \cite{evans2001} and having the ability to control the propagation of waves \cite{phani2006} as well as heat flow. \cite{lu1998,ashby1997,evans1998} Generally speaking, the properties and functionality of such materials are  dictated by the node connectivity. In particular, a minimum node connectivity of 6 is required for 2D lattice materials to be  stretching-dominated, and therefore,  more weight-efficient for structural applications. \cite{deshpande2001} As such, lattice materials with square architecture (which has a node connectivity of 4) are known to be very unstable when loaded along specific directions (as the only shear resistance arises from the joints) \cite{gibson1999} and typically require diagonal bracings to stabilize them.

@@

We started by testing samples of the four considered designs comprising
a tessellation of $6\times6$ square cells with $L=$ \KB{??} mm. The samples were fabricated with a multi-material \mf{@Katia: what do you mean multi-material} 3D printer \mf{(add model @James)} using \KB{name of material} \mf{add info here @James} and compressed uniaxially  using  an Instron Model 5969 with 50kN capacity  (\Cref{Fig2}(e)). \KB{switch labels (f) and (e) in Fig 2} %Using this set-up, we tested three replicas of each design that were 3D printed and tested on different days.
The results reported in \Cref{Fig2}(f)  show that all structures are characterized by an initial linear behavior, a sudden departure from linearity caused by in-plane buckling and catastrophic failure following immediately thereafter.   Furthermore, it is also important to note that all  designs with diagonal reinforcement (i.e. \emph{Designs A-C}) overlay each other in the linear regime. Focusing on the initial linear regime, we find that  the different diagonal reinforcement designs considered do not impact the structure's overall stiffness (i.e. the initial stiffness of Designs A, B and C is identical). Design D, as expected, has a higher stiffness because of its thicker vertical and horizontal element's. However, it fails much earlier due to a shorter critical buckling strain. On the other hand, \emph{Design A} (the sponge design) outperforms the  considered structures in the amount of load it can bare before the onset of buckling occurs and provides the best mechanical performance without compromising the structural stiffness.

>>>>

The macro-scale architecture of the \textit{Euplectella Asperguillum} provides a remarkable example of slender and regular lattice-like material constructed by nature. Such lattice materials have recently demonstrated to offer novel and unique properties, including being light weight, \cite{schaedler2011,ashby2006} having high energy absorption, \cite{evans2001} and having the ability to control the propagation of waves \cite{phani2006} as well as heat flow. \cite{lu1998,ashby1997,evans1998} Generally speaking, the properties and functionality of such materials are  dictated by the node connectivity. In particular, a minimum node connectivity of 6 is required for 2D lattice materials to be  stretching-dominated, and therefore,  more weight-efficient for structural applications. \cite{deshpande2001} As such, lattice materials with square architecture (which has a node connectivity of 4) are known to be very unstable when loaded along specific directions (as the only shear resistance arises from the joints) \cite{gibson1999} and typically require diagonal bracings to stabilize them.\cite{phani2017}

@@

We started by testing samples of the four considered designs comprising
a tessellation of $6\times6$ square cells with $L=1.91$ cm. The samples were fabricated with a multi-material 3D printer \mf{(add model @James)} using \KB{name of material} \mf{add info here @James} and compressed uniaxially  using  an Instron Model 5969 with 50kN capacity  (\Cref{Fig2}(e)). \KB{switch labels (f) and (e) in Fig 2} %Using this set-up, we tested three replicas of each design that were 3D printed and tested on different days.
The results reported in \Cref{Fig2}(f)  show that all structures are characterized by an initial linear behavior, a sudden departure from linearity caused by in-plane buckling and catastrophic failure following immediately thereafter.   Furthermore, it is also important to note that all  designs with diagonal reinforcement (i.e. \emph{Designs A-C}) overlay each other in the linear regime. Focusing on the initial linear regime, we find that  the different diagonal reinforcement designs considered do not impact the structure's overall stiffness (i.e. the initial stiffness of Designs A, B and C is identical). Design D, as expected, has a higher stiffness because of its thicker vertical and horizontal element's. However, it fails much earlier due to a shorter critical buckling strain. On the other hand, \emph{Design A} (the sponge design) outperforms the  considered structures in the amount of load it can bare before the onset of buckling occurs and provides the best mechanical performance without compromising the structural stiffness.

### 2018-12-05 Supplemental-FernandesWeaverBertoldi_AdvMaterials_2018.tex
changes

\begin{figure}[H]
    \centering
    \includegraphics[width=0.4\linewidth]{SFig2.png}
    \caption{{\bf Unit cell for Design A.} This design is inspired by the sponge structure and consists of a square grid  reinforced by a double diagonal system. The horizontal and vertical struts have length $L$ and circular cross section with diameter $D_{A,nd}$ and, as with the sponge, we assume $D_{A,nd}/L=0.1$. The diagonal elements have a circular cross section  with diameter $D_{A,d}=2 D_{A,nd}$.}
    \label{DesignA}
\end{figure}

@@

In this study we used CMA-ES to identify \begin{itemize} 
\item the number of diagonals, $N$
\item the volume ratio  of non-diagonal to diagonal members, $\lambda=V_{nd}/V_{d}$.
\item  the separation between each even set of diagonals, $S_i$ (see Fig. \ref{OptimizationSchematic})
\end{itemize}
resulting in a lattice structure with the large critical load. For such optimization problem, the number of optimization variables increases with the number of diagonals incorporated in the model(i.e. the total number of parameters are $1+ \frac{1}{2}(N - (N \text{ mod } 2))$ for a given optimization instance with $N$ number of diagonals).  Note, for simulations with odd number of diagonal reinforcements, only an even number of diagonals are separated while keeping one diagonal going through the non-diagonal junction in order to ensure geometry symmetry (see Fig. \ref{OptimizationSchematic}).

@@

\mf{Add table with optimal parameters results for each N, for both circular and rectangular cross-sections}

@@

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\linewidth]{SFig2}
    \caption{{\bf Unit cell for Design A.} This design is inspired by the sponge structure and consists of a square grid  reinforced by a double diagonal system. The horizontal and vertical struts have length $L$ and circular cross section with diameter $D_{A,nd}$ and, as with the sponge, we assume $D_{A,nd}/L=0.1$. The diagonal elements have a circular cross section  with diameter $D_{A,d}=2 D_{A,nd}$.}
    \label{DesignA}
\end{figure}

@@

In this study we used CMA-ES to identify \begin{itemize} 
\item the number of diagonals, $N$
\item the volume ratio  of non-diagonal to diagonal members, $\lambda=V_{nd}/V_{d}$.
\item  the separation between each even set of diagonals, $S_i$ (see Fig. \ref{OptimizationSchematic})
\end{itemize}
resulting in a lattice structure with the largest critical load. For such optimization problem, the number of optimization variables increases with the number of diagonals incorporated in the model(i.e. the total number of parameters are $1+ \frac{1}{2}(N - (N \text{ mod } 2))$ for a given optimization instance with $N$ number of diagonals).  Note, for simulations with odd number of diagonal reinforcements, only an even number of diagonals are separated while keeping one diagonal going through the non-diagonal junction in order to ensure geometry symmetry (see Fig. \ref{OptimizationSchematic}).

@@

\begin{table}[!htb]
\centering
    \begin{tabular}{c||c|c|c|c|c}
          & $\lambda$ & $S_1$ &$S_2$ &$S_3$&$S_4$ \\ \hline\hline
         $N=1$ &  3.1454 &  &  &  &  \\ \hline
         $N=2$ &  0.5614 &  0.3390 &  &  &  \\ \hline
         $N=3$ &  1.4784 &  0.2440 &  &  &  \\ \hline
         $N=4$ &  1.0151 &  0.0989 &  0.3358 &  &  \\ \hline
         $N=5$ &  0.9509 &  0.1733 &  0.3260 &  &  \\ \hline
         $N=6$ &  0.2009 &  0.2628 &  0.5827 &  0.8881 &  \\ \hline
         $N=7$ &  0.2962 &  0.4197 &  0.6917 &  0.9126 &  \\ \hline
         $N=8$ &  0.3263 &  0.1553 &  0.5533 &  0.7095 &  0.9113 \\
    \end{tabular}
\caption{Buckling Load Optimization}
\label{table1}
\end{table}

\begin{table}[!htb]
\centering
    \begin{tabular}{c||c|c|c|c|c}
          & $\lambda$ & $S_1$ &$S_2$ &$S_3$&$S_4$ \\ \hline\hline
         $N=1$ &  0.8908 &  &  &  &  \\ \hline
         $N=2$ &  0.4157 &  0.3233 &  &  &  \\ \hline
         $N=3$ &  0.3402 &  0.3268 &  &  &  \\ \hline
         $N=4$ &  0.2271 &  0.6103 &  0.7923 &  &  \\ \hline
         $N=5$ &  0.2772 &  0.2511 &  0.4076 &  &  \\ \hline
         $N=6$ &  0.1764 &  0.2785 &  0.5743 &  0.8675 &  \\ \hline
         $N=7$ &  0.1810 &  0.2899 &  0.5711 &  0.8443 &  \\ \hline
         $N=8$ &  0.1023 &  0.1459 &  0.3317 &  0.5561 &  0.7843 \\
    \end{tabular}
\caption{Buckling Strain Optimization}
\label{table2}
\end{table}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{SFig16.pdf}
	\caption{{\bf Stress Concentration.} Highest Misses Stress for different designs: Design A -- $3.362\times 10^{-2}$, Design B -- $4.362\times 10^{-2}$, Design C -- $4.165\times 10^{-2}$, Design D -- $3.550\times 10^{-2}$.}
	\label{asdfgdfsgasasdf}
\end{figure}
